Extended Data

### 2022-02-23 doc/manuscript/Dow_manuscript_Nature.Rmd
updated results section

For ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the CTW resulted in earlier achievement of phenological milestones.
Consistent with findings from previous studies[@parmesan_globally_2003;@ibanez_forecasting_2010;@friedl_tale_2014], leaf phenological milestones advanced at both sites (Fig. `r DOY_timing`a-b, `r EDT_phenology_parameters`), with greenup (DOY when EVI2 first crossed 15% of the segment EVI2 amplitude) advancing 3.45 days/$^\circ$C at SCBI (p=0.016) and 2.4 days/ $^\circ$C at Harvard Forest (p=0.1).
Similarly, at both sites, the stem growth milestones $DOY_{25}$, $DOY_{50}$, and $DOY_{g_{max}}$ all decreased with mean $T_{max}$ during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`c-d; `r EDF_pheno_all`).
Specifically, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ advanced 1.1-1.9 days/ $^\circ$C for ring-porous species and 3.5-3.6 days/ $^\circ$C for diffuse-porous species at SCBI, and 2.8-7.2 days/ $^\circ$C for ring-porous species and 6.6-7.9 days/ $^\circ$C for diffuse-porous species at Harvard Forest (`r EDT_phenology_parameters`).

@@

In contrast to the pronounced effects of $T_{max}$ on the timing of growth, its effects on $g_{max}$ and $\Delta DBH$ were weak and inconsistent (Figs. `r schematic_summary`, `r EDF_pheno_all`). 
Specifically, $g_{max}$, which occurred very close to $DOY_{50}$ (on $DOY_{g.max}$; `r EDT_phenology_parameters`), displayed either no relationship to mean $T_{max}$ during the critical temperature window (SCBI), or extremely small changes in opposite directions for ring- and diffuse- porous species (Harvard Forest).
$\Delta DBH$ displayed no relationship with mean $T_{max}$ during the critical temperature window (`r EDF_pheno_Tmax_climwin`).

>>>>

For ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the CTW resulted in earlier achievement of phenological milestones.
Consistent with findings from previous studies[@parmesan_globally_2003;@ibanez_forecasting_2010;@friedl_tale_2014], leaf phenological milestones advanced at both sites (Fig. `r DOY_timing`a-b, `r EDT_phenology_parameters`), with greenup (DOY when EVI2 first crossed 15% of the segment EVI2 amplitude) advancing 3.45 days/$^\circ$C at SCBI (p=0.016) and 2.4 days/ $^\circ$C at Harvard Forest (p=0.1).
Similarly, with the exception of ring-porous $DOY_{75}$ at SCBI and ring-porous $DOY_{g_{max}}$ at HF, the stem growth milestones $DOY_{25}$, $DOY_{50}$, $DOY_{75}$,  and $DOY_{g_{max}}$ decreased with mean $T_{max}$ during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`c-d; `r EDF_pheno_all`).
Specifically, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ advanced 0-1.7 days/ $^\circ$C for ring-porous species and 2.8-2.9 days/ $^\circ$C for diffuse-porous species at SCBI, and 10.3-12.3 days/ $^\circ$C for ring-porous species and 0.9-4.2 days/ $^\circ$C for diffuse-porous species at Harvard Forest (`r EDT_phenology_parameters`).

@@

In contrast to the pronounced effects of $T_{max}$ on the timing of growth, its effects on $g_{max}$ and $\Delta DBH$ were weak and inconsistent (Figs. `r schematic_summary`, `r EDF_pheno_all`). 
Specifically, $g_{max}$, which occurred very close to $DOY_{50}$ (on $DOY_{g.max}$; `r EDT_phenology_parameters`), displayed extremely small negative changes (HF) or changes in opposite directions (SCBI) in relationship to mean $T_{max}$ during the critical temperature window for ring- and diffuse- porous species.
$\Delta DBH$ displayed a weak positive relationship (+0.029-0.08 mm/ $^\circ$C) with mean $T_{max}$ during the critical temperature window at SCBI and a weak negative relationship (-0.2-0.03mm/ $^\circ$C) at HF (`r EDF_pheno_Tmax_climwin`).
